Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-06 paper/tex/sections/appendix.tex
add eccentric dco on sc plot

>>>>

\subsection{Distribution of eccentric sources on sensitivity curve}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}
